Porting the Steel Bank Common Lisp Compiler and Runtime to the Nintendo Switch NX Platform

### 2025-02-25 els2025-sbcl-nx/paper.tex
Mention the switch 2

>>>>

The follow-up console to the Nintendo Switch, called ``Switch 2'' has also recently been announced. The device is backwards compatible with the NX and we expect that the operating environment will be very similar if not identical to that of the NX, just with more RAM and a better CPU and GPU. We hope to receive developer access to the Switch 2 and ensure that the port works for that, too.
